---
title: "Introduction"
  subtitle: "R for Data Science"
  date: "9/19/2025"
format: html
editor: visual
---

## Data Visualization

### 1.1 Introduction

This chapter will teach you how to visualize your data using ggplot2.

```{r}
library(tidyverse) # load the tidyverse packages
library(palmerpenguins) # for this chapter, we'll use palmerpenguins and ggthemes
library(ggthemes)
```

### 1.2 First steps

-   A **data frame** is a rectangular collection of variables (in the columns) and observations (in the rows).

-   A **variable** is a quantity, quality, or property that you can measure.

-   A **value** is the state of a variable when you measure it. The value of a variable may change from measurement to measurement.

-   An **observation** is a set of measurements made under similar conditions (you usually make all of the measurements in an observation at the same time and on the same object). An observation will contain several values, each associated with a different variable. We’ll sometimes refer to an observation as a data point.

-   **Tabular data** is a set of values, each associated with a variable and an observation. Tabular data is *tidy* if each value is placed in its own “cell”, each variable in its own column, and each observation in its own row.

```{r}
palmer::penguins # use the penguins data frame found in palmerpenguins

penguins  #this prints a tibble of its contents
glimpse(penguins) #alternative view to see all variables and first few observations of each
View(penguins) # to open interactive data viewer
```

Among the variables in `penguins` are:

1.  `species`: a penguin’s species (Adelie, Chinstrap, or Gentoo).

2.  `flipper_length_mm`: length of a penguin’s flipper, in millimeters.

3.  `body_mass_g`: body mass of a penguin, in grams.

```{r}
?penguins #learn more about the dataset
```

#### 1.2.2 Ultimate goal

The ultimate goal in this chapter is to recreate a visualization displaying the relationship between flipper lengths and body masses of these penguins, taking into consideration the species of the penguin.

#### 1.2.3 Creating a ggplot

```{r}
# creating a ggplot

ggplot(data = penguins) #blank 

# use the mapping argument to define how variables in your dataset at mapped to visual properties (aesthetics) of your plot

ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g)
) #not yet articilauted how to represent the observations from our data frame on our plot

#| fig-alt: |
ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g)
) +
  geom_point() #scatterplot
# we recieve warning message because there are two penguins in our dataset with missing values and ggplot2 has no way of representing them on the plot without both of these values.
```

#### 1.2.4 Adding aesthetics and layers

```{r}
#| warning: false
#| fig-alt: |
ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g, color = species)
) +
  geom_point()
```
